Figures to insert in text

### 2018-02-25 Chapters/Chapter02.tex
Linhares figs

>>>>

\begin{figure}[h!]
  \centering
  \subfloat[$z \in \{.1, .2, .3, .4, .5, 1\}$]{\includegraphics[width=2.9in]{./images02/new-images/iter_z_01-05.png}}
  \subfloat[$z \in \{1.5, 3, 4.5, 6\}$]{\includegraphics[width=2.9in]{./images02/new-images/z_15_3_45_6.png}}

  \subfloat[$z \in \{0, 1\}$]{\includegraphics[width=2.9in]{./images02/new-images/z_0_1.png}}
  \subfloat[$z \in \{0, 0.5, 1, 1.5, 3, 4.5, 6\}$]{\includegraphics[width=2.9in]{./images02/new-images/iter_z_all_2.png}}

  \caption{(a) and (b) show the behavior of a single read; (c) and (d) present the effects of 6 iterative reads. As stated previously, we can see a deterioration of convergence, with lower critical distance as $z>1$.  Another observation can be made here, concerning the discrepancy of Kanerva's Fig 7.3 and our data.  It seems that Kanerva did not consider that a single read would only `clean' a small number of dimensions \emph{after the critical distance}. What we observe clearly is that with a single read, as the distance grows, the system only `cleans' towards the orthoghonal distance 500 after a number of iterative readings.}
  \label{fig:murillo-generalization-experiments}
\end{figure}

Physicist Paulo Murilo observed that the models of Kanerva-read ($z=1$) and Chada-read ($z=0$) were simple variations of the exponent $z$, which suggests experimenting with different values. The results, however, have not yielded performance improvements.  Though for $z \leq 1$ results are comparable to $z=1$, for $z>1$, the system shows a clear deterioration, with a smaller distance to convergence and higher divergence at large-distance reads. This is shown in Figure \ref{fig:murillo-generalization-experiments}.

### 2018-02-25 Chapters/sdm2.tex
Linhares figs

>>>>

\begin{figure}[h!]
\centering

\subfloat[Kanerva's original model]{\includegraphics[width=3.1in]{./images02/new-images/kanerva-read.png}}

\subfloat[Chada's read]{\includegraphics[width=3.1in]{./images02/new-images/chada-read_z_0.png}}
\caption{How far, in hamming distance, is a read item from the original stored item? Kanerva demonstrated that, after a small number of iterative readings (6 here), a critical distance behavior emerges. Items read at close distance converge rapidly; whereas farther items do not converge. Most striking is the point in which the system displays the tip-of-tongue behavior. Described by psychological moments when some features of the item are prominent in one's thoughts, yet the item still cannot be recalled (but an additional cue makes convergence `immediate'). Mathematically, this is the precise distance in which, despite having a relatively high number of cues (correct bits) about the desired item, the time to convergence is infinite.   Heatmap colors display the hamming distance the associative memory is able to cleanly converge to---or not.   In the $x$-axis, the distance from the desired item is displayed. In the $y$-axis, we display the read operation's behavior as the number of items registered in the memory grows.  These graphs are computing intensive, yet they can be easily tested by readers in our provided jupyter notebooks. Note the different scales.}
\label{fig:crit-dist-10k-writes}

\end{figure}

Figure \ref{fig:crit-dist-10k-writes} compares the critical distance behavior under different scenarios.  This replicates our previous results and is a first part of the process of framework validation, to which we throw our attention next.

### 2018-02-25 linhares-figs-captions.tex
Linhares figs

% FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES
\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/z_0_15_3.jpg}
  \caption{z  0  15  3.jpg}
  \label{fig:boat1}
\end{figure}

Figure \ref{fig:boat1} shows a boat.

/images02/new-images/

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/z_all.jpg}
  \caption{z  all.jpg}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/iter_z_0_05_1.png}
  \caption{iter z  0  0.5 1.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/iter_z_01-05.png}
  \caption{iter z 01-05.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/iter_z_05_1_15_3.png}
  \caption{iter z  0.5 1 1.5 3.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/iter_z_05_1_15.png}
  \caption{iter $z\in \{0.5, 1, 1.5\}$ }
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/iter_z_all_2.png}
  \caption{iter z all 2.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/iter_z_all.png}
  \caption{iter z all.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/z_0_1.png}
  \caption{z 0 1.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/z_1_15_3_45_6.png}
  \caption{z 1 1.5 3 4.5 6.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/z_01-05.png}
  \caption{z 01 - 05.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/z_15_3_45_6.png}
  \caption{z 1.5 3 4.5 6.png}
  \label{fig:boat1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/z_15_3_45.png}
  \caption{z 1.5 3 4.5.png}
  \label{fig:boat1}
\end{figure}

faltando as imagens do google doc...
\section{Critical Distance}

@@

\subfloat[]{\includegraphics[width=3.1in]{./images02/new-images/kanerva-read.png}}

\subfloat[]{\includegraphics[width=3.1in]{./images02/new-images/chada-read_z_0.png}}

\caption{The critical distance behavior, as the memory is written with items.  The colors of this heatmap display the hamming distance to the item being read as a function of the distance from that item and the numbers of items registered in memory.  In the $x$-axis, the distance from the item being read is displayed. In the $y$-axis, we display the read operation's behavior as the number of items registered in the memory grows.  In (a), we have Kanerva's original model; whereas (b) displays Chada's read.}
\label{fig:crit-dist-10k-writes}

@@

@@

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/information_decay.png}
  \caption{information decay 4.png}
  \label{fig:boat1}
\end{figure}

>>>>

% FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES
\begin{figure}[h!]
  \centering
  \subfloat[$z \in \{.1, .2, .3, .4, .5, 1\}$]{\includegraphics[width=2.9in]{./images02/new-images/iter_z_01-05.png}}
  \subfloat[$z \in \{1.5, 3, 4.5, 6\}$]{\includegraphics[width=2.9in]{./images02/new-images/z_15_3_45_6.png}}

  \subfloat[$z \in \{0, 1\}$]{\includegraphics[width=2.9in]{./images02/new-images/z_0_1.png}}
  \subfloat[$z \in \{0, 0.5, 1, 1.5, 3, 4.5, 6\}$]{\includegraphics[width=2.9in]{./images02/new-images/iter_z_all_2.png}}

  \caption{Physicist Paulo Murillo observed that the models of Kanerva-read ($z=1$) and Chada-read ($z=0$) were simple variations of the exponent $z$, which suggests experimenting with different values. The results, however, have not yielded performance improvements.  Though for $z \leq 1$ results are comparable to $z=1$, for $z>1$, the system shows a clear deterioration, with a smaller distance to convergence and higher divergence at large-distance reads. (a) and (b) show the behavior of a single read; (c) and (d) present the effects of 6 iterative reads. As stated previously, we can see a deterioration of convergence, with lower critical distance as $z>1$.  Another observation can be made here, concerning the discrepancy of Kanerva's Fig 7.3 and our data.  It seems that Kanerva did not consider that a single read would only `clean' a small number of dimensions \emph{after the critical distance}. What we observe clearly is that with a single read, as the distance grows, the system only `cleans' towards the orthoghonal distance 500 after a number of iterative readings.}
  \label{fig:murillo-generalization-experiments}
\end{figure}

% FIGURES ITER FIGURES ITER FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES FIGURES

\section{Critical Distance Analysis: a brief review}

@@

\subfloat[Kanerva's original model]{\includegraphics[width=3.1in]{./images02/new-images/kanerva-read.png}}

\subfloat[Chada's read]{\includegraphics[width=3.1in]{./images02/new-images/chada-read_z_0.png}}
\caption{How far, in hamming distance, is a read item from the original stored item? Kanerva demonstrated that, after a small number of iterative readings (6 here), a critical distance behavior emerges. Items read at close distance converge rapidly; whereas farther items do not converge. Most striking is the point in which the system displays the tip-of-tongue behavior. Described by psychological moments when some features of the item are prominent in one's thoughts, yet the item still cannot be recalled (but an additional cue makes convergence `immediate'). Mathemathically, this is the precise distance in which, despite having a relatively high number of cues (correct bits) about the desired item, the time to convergence is infinite.   Heatmap colors display the hamming distance the associative memory is able to cleanly converge to---or not.   In the $x$-axis, the distance from the desired item is displayed. In the $y$-axis, we display the read operation's behavior as the number of items registered in the memory grows.  These graphs are computing intensive, yet they can be easily tested by readers in our provided jupyter notebooks. Note the different scales.}
\label{fig:crit-dist-10k-writes}

@@

Figure \ref{fig:Crit-Dist-Comparison} compares the critical distance behavior under different scenarios.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{./images02/new-images/information_decay.png}
  \caption{information decay 4.png}
  \label{fig:boat10}
\end{figure}
